---
title: "JIACRA IV"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE, message = FALSE, warning = FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(comment = NA)
```

```{r settings, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
# This R markdown file contains all the univariate analyses performed for the elaboration of the JIACRA IV report. Please use the knit option to generate a structured word document containing a summary of all analyses.

# Cleaning the desk (removing all objects)
rm(list=ls())

# Set working directory
setwd('X:/Your/Path/Directory"')

## Config ------------------------------------------------------------------
source("config.R")

## Import data ------------------------------------------------------------
AMCh_AMRh <- read.csv("data/AMCh_AMRh.csv")
AMCa_AMRh <- read.csv("data/AMCa_AMRh.csv")
AMRa_AMRh <- read.csv("data/AMRa_AMRh.csv")
AMCa_AMRa <- read.csv("data/AMCa_AMRa.csv")

## Analysis function ------------------------------------------------------------
source("scripts/univariate_analysis.R")

```

$~$

## Chapter 5. Results for carbapenems

### 5.2 Consumption in humans and resistance in bacteria from humans

```{r 5.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(dat=AMCh_AMRh,dataset_type = "AMCh_AMRh", model="log",class="CAR",pathogen="ESCCOL",ymax=0.25,years=c(2019,2020,2021)) 
## Klepne
analysis_fun(AMCh_AMRh,"AMCh_AMRh",model="log",class="CAR",pathogen="KLEPNE",ymax=1,years=c(2019,2020,2021)) 
```

$~$

## Chapter 6. Results for 3rd and 4th generation cephalosporins

### 6.2 Consumption in humans and resistance in bacteria from humans

```{r 6.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCh_AMRh, "AMCh_AMRh", model="log",class="CEPH",pathogen="ESCCOL",ymax=0.5, years=c(2019,2020,2021)) 
```
### 6.3.  Consumption in food-producing animals and resistance in bacteria from food-producing animals

```{r 6.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="CEPH",pathogen="ESCCOL", animal="animals",ymax=0.25, years=c(2019,2020,2021)) 
analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="CEPH",pathogen="ESCCOL", animal="pigs", ymax=0.25,years=c(2019,2021)) 

## ESBL-AmpC
analysis_fun(dat=AMCa_AMRa,dataset_type="AMCa_AMRa",class="CEPH",pathogen="ESCCOL", animal="ESBL", ymax=1, years=c(2019,2020,2021)) 
```


### 6.4 Resistance in bacterial isolates from humans and food-producing animals

```{r 6.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMRa_AMRh,"AMRa_AMRh", class="CEPH",pathogen="ESCCOL", animal="pigs",ymax=0.5, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh,"AMRa_AMRh", model = "log", class="CEPH",pathogen="ESCCOL", animal="calves",ymax=0.5, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh,"AMRa_AMRh", class="CEPH",pathogen="ESCCOL", animal="turkeys",ymax=0.5, years=2020) 
analysis_fun(AMRa_AMRh,"AMRa_AMRh", class="CEPH",pathogen="ESCCOL", animal="broilers",ymax=0.5, years=2020) 
```

### 6.5 Consumption in food-producing animals and resistance in bacteria from humans

```{r 6.5, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="CEPH",pathogen="ESCCOL",ymax=0.5, years=c(2019,2020,2021)) 
```
$~$

## Chapter 7. Results for fluoroquinolones 

### 7.2 Consumption in humans and resistance in bacteria from humans

```{r 7.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCh_AMRh, "AMCh_AMRh",model="log",class="QALL",pathogen="ESCCOL",ymax=1, years=c(2019,2020,2021)) 
## CAMJEJ
analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="QALL",pathogen="CAMJEJ",ymax=1.1, years=c(2019,2020,2021)) 
## CAMCOL
analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="QALL",pathogen="CAMCOL",ymax=1.1, years=c(2019,2020,2021))
```
### 7.3.  Consumption in food-producing animals and resistance in bacteria from food-producing animals

```{r 7.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="QALL",pathogen="ESCCOL", animal="animals",ymax=1, years=c(2019,2020,2021)) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="QALL",pathogen="ESCCOL", animal="poultry", ymax=1,years=2020) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="QALL",pathogen="ESCCOL", animal="pigs", ymax=1,years=c(2019,2021)) 
# CAMJEJ
analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="QALL",pathogen="CAMJEJ", animal="poultry", ymax=1,years=2020) 
# CAMCOL
analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="QALL",pathogen="CAMCOL", animal="pigs", ymax=1,years=2021) 
```

### 7.4 Resistance in bacterial isolates from humans and food-producing animals

```{r 7.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="QALL",pathogen="ESCCOL", animal="pigs",ymax=1, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh", model="log",class="QALL",pathogen="ESCCOL", animal="calves",ymax=1, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="QALL",pathogen="ESCCOL", animal="turkeys",ymax=0.5,  years=2020) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="QALL",pathogen="ESCCOL", animal="broilers",ymax=0.5, years=2020) 

## CAMJEJ
analysis_fun(AMRa_AMRh, "AMRa_AMRh", class="QALL",pathogen="CAMJEJ", animal="turkeys",ymax=1, years=2020, model='log') 
analysis_fun(AMRa_AMRh, "AMRa_AMRh", model = "log", class="QALL",pathogen="CAMJEJ", animal="broilers",ymax=1, years=2020) 

## CAMCOL
analysis_fun(AMRa_AMRh, "AMRa_AMRh", class="QALL",pathogen="CAMCOL", animal="pigs", ymax=1.1, years=2021) 

```

### 7.5 Consumption in food-producing animals and resistance in bacteria from humans
```{r 7.5, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="QALL",pathogen="ESCCOL",ymax=1, years=c(2019,2020,2021)) 

## CAMJEJ
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="QALL",pathogen="CAMJEJ",ymax=1.1, years=c(2019,2020,2021))
## CAMCOL
analysis_fun(AMCa_AMRh, "AMCa_AMRh",model="log",class="QALL",pathogen="CAMCOL",ymax=1.1, years=c(2019,2020,2021))
```
$~$

## Chapter 8. Results for polymixins 

### 8.3.  Consumption in food-producing animals and resistance in bacteria from food-producing animals

```{r 8.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="POL",pathogen="ESCCOL", animal="animals",ymax=0.25, years=c(2019,2020,2021)) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="POL",pathogen="ESCCOL", animal="poultry", ymax=0.25,years=2020) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",model="log",class="POL",pathogen="ESCCOL", animal="pigs", ymax=0.25,years=c(2019,2021)) 
```

## Chapter 9. Results for aminopenicillins

### 9.2 Consumption in humans and resistance in bacteria from humans

```{r 9.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
# # E.Coli
 analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="AMP",pathogen="ESCCOL",ymax=1, years=c(2019,2020,2021))
```

### 9.3.  Consumption in food-producing animals and resistance in bacteria from food-producing animals

```{r 9.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="AMP",pathogen="ESCCOL", animal="animals",ymax=1, years=c(2019,2020,2021)) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="AMP",pathogen="ESCCOL", animal="poultry", ymax=1,years=2020) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="AMP",pathogen="ESCCOL", animal="pigs", ymax=1,years=c(2019,2021)) 
```

### 9.4 Resistance in bacterial isolates from humans and food-producing animals

```{r 9.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="AMP",pathogen="ESCCOL", animal="pigs",ymax=1, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="AMP",pathogen="ESCCOL", animal="calves",ymax=1, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="AMP",pathogen="ESCCOL", animal="turkeys",ymax=1, years=2020) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="AMP",pathogen="ESCCOL", animal="broilers",ymax=1, years=2020) 
```

### 9.5 Consumption in food-producing animals and resistance in bacteria from humans
```{r 9.5, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="AMP",pathogen="ESCCOL",ymax=1, years=c(2019,2020,2021)) 
```
$~$

## Chapter 10. Results for macrolides

### 10.2 Consumption in humans and resistance in bacteria from humans

```{r 10.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## CAMJEJ
analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="MAC",pathogen="CAMJEJ",ymax=0.25, years=c(2019,2020,2021)) 
## CAMCOL
analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="MAC",pathogen="CAMCOL",ymax=1, years=c(2019,2020,2021)) 
```

### 10.3.  Consumption in food-producing animals and resistance in bacteria from food-producing animals

```{r 10.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
# CAMJEJ
analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="MAC",pathogen="CAMJEJ", animal="poultry", ymax=0.25,years=2020) 

# CAMCOL
analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="MAC",pathogen="CAMCOL", animal="pigs", ymax=1,years=2021) 
```


### 10.4 Resistance in bacterial isolates from humans and food-producing animals
```{r 10.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## CAMJEJ
analysis_fun(AMRa_AMRh, "AMRa_AMRh", model = "log", class="MAC",pathogen="CAMJEJ", animal="turkeys", ymax=0.25,years=2020) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh", model = "log", class="MAC",pathogen="CAMJEJ", animal="broilers", ymax=0.25,years=2020) 

## CAMCOL
analysis_fun(AMRa_AMRh, "AMRa_AMRh", model="log", class="MAC",pathogen="CAMCOL", animal="pigs", ymax=1,years=2021)
```

### 10.5 Consumption in food-producing animals and resistance in bacteria from humans
```{r 10.5, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## CAMJEJ
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="MAC",pathogen="CAMJEJ",ymax=0.25, years=c(2019,2020,2021))
## CAMCOL
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="MAC",pathogen="CAMCOL",ymax=1, years=c(2019,2020,2021))
```

$~$

## Chapter 11. Results for tetracyclines

### 11.2 Consumption in humans and resistance in bacteria from humans

```{r 11.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## CAMJEJ
analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="TET",pathogen="CAMJEJ",ymax=1, years=c(2019,2020,2021)) 
## CAMCOL
analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="TET",pathogen="CAMCOL",ymax=1.1, years=c(2019,2020,2021)) 
```

### 11.3.  Consumption in food-producing animals and resistance in bacteria from food-producing animals

```{r 11.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="TET",pathogen="ESCCOL", animal="animals",ymax=1, years=c(2019,2020,2021)) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="TET",pathogen="ESCCOL", animal="poultry", ymax=1,years=2020) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="TET",pathogen="ESCCOL", animal="pigs", ymax=1,years=c(2019,2021)) 
# CAMJEJ
analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="TET",pathogen="CAMJEJ", animal="poultry", ymax=1,years=2020) 
# CAMCOL
analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="TET",pathogen="CAMCOL", animal="pigs", ymax=1.1,years=2021) 
```

### 11.4 Resistance in bacterial isolates from humans and food-producing animals
```{r 11.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## CAMJEJ
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="TET",pathogen="CAMJEJ", animal="turkeys", ymax=1,years=2020) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="TET",pathogen="CAMJEJ", animal="broilers", ymax=1.1,years=2020) 

## CAMCOL
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="TET", pathogen="CAMCOL", animal="pigs", ymax=1.1, years=2021)
```

### 11.5 Consumption in food-producing animals and resistance in bacteria from humans

```{r 11.5, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## CAMJEJ
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="TET",pathogen="CAMJEJ",ymax=1, years=c(2019,2020,2021))
## CAMCOL
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="TET",pathogen="CAMCOL",ymax=1.1, years=c(2019,2020,2021))
```

$~$

## Chapter 13. Antimicrobial consumption and proportion of complete susceptibility in Escherichia coli 

### 13.1 Consumption in animals and resistance in food-producing animals
```{r FullyS_1, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(dat = AMCa_AMRa, dataset_type = "AMCa_AMRa", model='log',class="CS", pathogen="ESCCOL", animal='animals',ymax=1, years=c(2019,2020,2021)) 
```

### 13.2 Consumption in humans and resistance in bacteria from humans
```{r FullyS_2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(dat = AMCh_AMRh, dataset_type = "AMCh_AMRh", class="CS", pathogen="ESCCOL", ymax=1, years=c(2019,2020,2021)) 
```

# 18. Annex – Salmonella spp. analyses 
## 18.2 Third- and fourth-generation cephalosporins 
### 18.2.1 Consumption in humans and resistance in Salmonella spp. isolates from humans
```{r 18.2.1, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCh_AMRh, "AMCh_AMRh", class="CEPH",pathogen="SLMSPP",ymax=0.25, years=c(2019,2020,2021)) 
```
### 18.2.2 Consumption in food-producing animals and resistance in Salmonella spp. isolates from food-producing animals 
```{r 18.2.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCa_AMRa, "AMCa_AMRa", class="CEPH",pathogen="SLMSPP",ymax=0.25, animal='animals',  years=c(2019,2020,2021)) 
## SalmSpp in pigs
analysis_fun(AMCa_AMRa, "AMCa_AMRa", class="CEPH",pathogen="SLMSPP",ymax=0.25, animal='pig carcasses', years=c(2019,2021)) 
```

### 18.2.3 	Resistance in Salmonella isolates from humans and food-producing animals
```{r 18.2.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP SIMR
analysis_fun(AMRa_AMRh, "AMRa_AMRh", class="CEPH",pathogen="SLMSPP",ymax=0.25, model = 'log', animal='SIMR',  years=c(2019,2020,2021)) 

## SalmSPP
analysis_fun(AMRa_AMRh, "AMRa_AMRh", model="log", class="CEPH",pathogen="SLMSPP", animal="pig carcasses", ymax=0.25, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh", model="log", class="CEPH",pathogen="SLMSPP", animal="turkeys", ymax=0.25,years=2020) 
analysis_fun(AMRa_AMRh,"AMRa_AMRh", model="log", class="CEPH",pathogen="SLMSPP", animal="broilers", ymax=0.25,years=2020) 

```
### 18.2.4	Consumption in food-producing animals and resistance of Salmonella spp. from humans

```{r 18.2.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCa_AMRh, "AMCa_AMRh", model="log", class="CEPH",pathogen="SLMSPP",ymax=0.25, years=c(2019,2020,2021)) 
```
## 18.3 Fluoroquinolones and other quinolones
### 18.3.1 Consumption in humans and resistance in Salmonella spp. isolates from humans
```{r 18.3.1, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCh_AMRh, "AMCh_AMRh", class="QALL",pathogen="SLMSPP",ymax=1, years=c(2019,2020,2021)) 
```
### 18.3.2 Consumption in food-producing animals and resistance in Salmonella spp. isolates from food-producing animals 
```{r 18.3.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCa_AMRa, "AMCa_AMRa", class="QALL",pathogen="SLMSPP",ymax=1, animal='animals',  years=c(2019,2020,2021)) 
analysis_fun(AMCa_AMRa, "AMCa_AMRa", class="QALL",pathogen="SLMSPP",ymax=1, animal='pig carcasses', years=c(2019,2021)) 
analysis_fun(AMCa_AMRa, "AMCa_AMRa", class="QALL",pathogen="SLMSPP",ymax=1,model = 'log', animal='poultry', years=2020)
```

### 18.3.3 	Resistance in Salmonella isolates from humans and food-producing animals
```{r 18.3.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
# SIMR
analysis_fun(dat=AMRa_AMRh,dataset_type="AMRa_AMRh",class="QALL",pathogen="SLMSPP", animal="SIMR", ymax=1, years=c(2019,2020,2021)) 

## SalmSPP
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="QALL",pathogen="SLMSPP", animal="pig carcasses", ymax=1, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="QALL",pathogen="SLMSPP", animal="turkeys", model='linear', ymax=0.25,years=2020) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="QALL",pathogen="SLMSPP", animal="broilers", ymax=0.5,years=2020) 
```
### 18.3.4	Consumption in food-producing animals and resistance of Salmonella spp. from humans

```{r 18.3.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="QALL",pathogen="SLMSPP",ymax=1, years=c(2019,2020,2021)) 
```
# 18.4	Polymyxins
## 18.4.1	Consumption and resistance of Salmonella spp., in food-producing animals
```{r 18.4.1, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="POL",pathogen="SLMSPP", animal='animals',ymax=1, years=c(2019,2020,2021)) 

analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="POL",pathogen="SLMSPP", animal='pig carcasses',ymax=1.1, years=c(2019,2021)) 
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="POL",pathogen="SLMSPP", animal='poultry',ymax=1, years=2020, model='quadratic')
```
# 18.5 Aminopenicillins

## 18.5.1	Consumption in humans and resistance in Salmonella spp. isolates from humans

```{r 18.5.1, results="asis", fig.width=10, fig.height=7, warning = FALSE}
# SalmSPP
analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="AMP",pathogen="SLMSPP",ymax=1, years=c(2019,2020,2021))
```

### 18.5.2  Consumption in food-producing animals and resistance in bacteria from food-producing animals

```{r 18.5.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## E.Coli
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="AMP",pathogen="SLMSPP", animal="animals",ymax=1, years=c(2019,2020,2021)) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="AMP",pathogen="SLMSPP", animal="poultry", model='linear', ymax=1,years=2020) 

analysis_fun(dat=AMCa_AMRa,dataset_type = "AMCa_AMRa",class="AMP",pathogen="SLMSPP", animal="pig carcasses", model='quadratic', ymax=1,years=c(2019,2021))
```

### 18.5.3 Resistance in bacterial isolates from humans and food-producing animals

```{r 18.5.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
# SIMR
analysis_fun(dat=AMRa_AMRh,dataset_type="AMRa_AMRh",class="AMP",pathogen="SLMSPP", animal="SIMR", ymax=1, years=c(2019,2020,2021)) 
## SalmSPP
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="AMP",pathogen="SLMSPP", animal="pig carcasses", ymax=1, years=c(2019,2021)) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="AMP",pathogen="SLMSPP", animal="turkeys", ymax=1, years=2020) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="AMP",pathogen="SLMSPP", animal="broilers", ymax=1, years=2020) 
```

### 18.5.4 Consumption in food-producing animals and resistance in bacteria from humans
```{r 18.5.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="AMP",pathogen="SLMSPP",ymax=1, years=c(2019,2020,2021)) 
```
$~$

## 18.6 Tetracyclines

### 18.6.1 Consumption in humans and resistance in bacteria from humans

```{r 18.6.1, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCh_AMRh, "AMCh_AMRh",class="TET",pathogen="SLMSPP",ymax=1, years=c(2019,2020,2021)) 
```

### 18.6.2  Consumption in food-producing animals and resistance in bacteria from food-producing animals

```{r 18.6.2, results="asis", fig.width=10, fig.height=7, warning = FALSE}
# SalmSPP
analysis_fun(AMCa_AMRa, "AMCa_AMRa",class="TET",pathogen="SLMSPP", animal="animals",ymax=1, years=c(2019,2020,2021)) 
analysis_fun(AMCa_AMRa, "AMCa_AMRa", class="TET",pathogen="SLMSPP",ymax=1, animal='pig carcasses',  years=c(2019,2021), model = 'quadratic')
analysis_fun(AMCa_AMRa, "AMCa_AMRa", class="TET",pathogen="SLMSPP",ymax=1, animal='poultry',  years=2020)
```


### 18.6.3 Resistance in bacterial isolates from humans and food-producing animals
```{r 18.6.3, results="asis", fig.width=10, fig.height=7, warning = FALSE}
# SIMR
analysis_fun(dat=AMRa_AMRh, dataset_type="AMRa_AMRh",class="TET",pathogen="SLMSPP", animal="SIMR", ymax=1, years=c(2019,2020,2021)) 
## SalmSPP
analysis_fun(AMRa_AMRh, "AMRa_AMRh",model = "log",class="TET",pathogen="SLMSPP", animal="pig carcasses", ymax=1, years=c(2019,2021))
analysis_fun(AMRa_AMRh, "AMRa_AMRh",model = "log",class="TET",pathogen="SLMSPP", animal="turkeys", ymax=1,years=2020) 
analysis_fun(AMRa_AMRh, "AMRa_AMRh",class="TET",pathogen="SLMSPP", animal="broilers", ymax=1,years=2020)

```

### 18.6.4 Consumption in food-producing animals and resistance in bacteria from humans
```{r 18.6.4, results="asis", fig.width=10, fig.height=7, warning = FALSE}
## SalmSPP
analysis_fun(AMCa_AMRh, "AMCa_AMRh",class="TET",pathogen="SLMSPP",ymax=1, years=c(2019,2020,2021)) 
```